---
title: "YYangEmily_PeerCommentary_Amandafwu_01"
author: "Amanda Wu"
date: "September 17, 2023"
output:
  rmarkdown::html_document:
    theme: cerulean
---

# Working with Other Data Structures
## Challenge 1
<br> 
Load libraries. 
Check package is downloaded: In Console x <- system.file(package = "tidyr") <br> Then type x. Should spit out where the package is installed. 
<br> [1] "/Library/Frameworks/R.framework/Versions/4.3-arm64/Resources/library/tidyr"<br> [1] "" = package not installed.<br>
https://hohenfeld.is/posts/check-if-a-package-is-installed-in-r/

```{r Challenge 1}
library(dplyr)
library(tidyr)
library(stringr)

# Enter the sentence. It is one object. 
v <- ("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed blah blah")
#Split the vector v using str_split. I'm telling it to split "space" so every word is split apart. 
x <- str_split(v, " ")
##on my Rstudio, str_split won't work as they "couldn't find the function" but it may just be my computer
x
# Make the string into 8x3 matrix. Need to add 2 words to the sentence because 22 not divisible by 3. 
m <- matrix(data = x[[1]] , nrow = 8, ncol = 3, byrow = TRUE)
m
# Pull out the third column which contains every third word. Ignoring the last blah
b <- m[c(1:7),c(3)]
##interesting and creative way of taking the third column! I used seq to take it out but I also like how efficient your method can be
b
```
## Challenge 2
<br> 
```{r Challenge 2}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
# Select columns 2,3,6. Comma before c 
x <- m[,c(2,3,6)]
x
# Select rows 6 to 8. Comma after c
x <- m[c(6:8),]
x
# Select row 2, column 2 to row 6, column 9. Select (2,2) to (6,9). Tell it between what rows and between what columns to take. 
x <- m[c(2:6),c(2:9)]
x

#Not used but could be useful in the future. Selecting data from matrix of different lengths. Make matrix from Row 2 and Column 9. 
library(qpcR) 
## for some reason, I could not open this package but it could be very beneficial if it works for you!
x <- m[,c(9)]
y <- m[c(2),]
dta <- qpcR:::cbind.na(x, y) #https://statisticsglobe.com/cbind-and-rbind-vectors-with-different-length-in-r
## good to include the link of the website where you learned this information
dta
```
## Challenge 3
<br> 
```{r Challenge 3}
a <- array(data = 400:1, dim = c(5,5,4,4))
#All 4 coordinates specified so return 1 value
a[1, 1, 1, 2]
# 3 coordinates specified and returns all possibilities of the 4th
a[2, 3, 2,]
# 2 dimensions have range so 2D
a[1:5, 1:5, 3, 3]
## good explanations, this was also how i made my array
```

## Challenge 4 
<br> Nested list but it looks horrible
```{r Challenge 4, }
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Anthropoidea
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Haplorhini
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini") 
Primates
Phylogeny <- list(Primates)
names(Phylogeny) <- list("Primates")
Phylogeny

##this is what i did too! nice job! 
```
## Challenge 5
<br> 
```{r Challenge 5}
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)

df <- m3
# Rename columns and rows for fun 
colnames(df) <- c("Column_1","Column_2","Column_3")
rownames(df) <- c("Row_1","Row_2","Row_3", "Row_4","Row_5")
df
#Convert column 2 to logic
l <- as.logical(df[,c(2)])
#Convert column 3 to factor
f <- as.factor(df[,c(3)])
#str tells you structure
str(l)
str(f)
## i think this is what i had done as well, besides naming the columns but good job! 
```

*I listed a few errors from my end that was occurring but for the most part, this was a really good job and you had great detail in your explanations! It could be helpful to add subheadings to your chunks to further divide your work. Great job! 